Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-02 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] finished bounds on scalar scenario, added posterior predictive except for most general scenario

\begin{figure*}
  \setlength{\relwidth}{0.31\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \caption{ The sensitivity to the tensorial coupling
      $\wilson{T}$ of $F_H$ [first row] and ${\cal B}$ [second row] in
      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ [fifth row] in $B^0 \to K^{*0}
      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
      last two rows, the observables are normalized by the lifetime of
      the $B$ meson for easier comparison with the branching
      ratios. The bands represent the theory uncertainties at 68\%
      and 95\% probability.  For comparison, two sets of bands are
      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
      latest 68\% uncertainty reported by LHCb (grey) if a measurement
      is available. }
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
%\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & only $\overline{\cal B}(B_s \to \bar\mu\mu)$
  & all
  \\
  set of couplings
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P',\,9,\,9',\,10,\,10'}$
  \\
  \hline \hline
  $\mbox{Re}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & $\quad$ $[-0.10,\, 0.08]$ ($[-0.14,\, 0.13]$) $\quad$
  & $\quad$ $[-0.08,\, 0.07]$ ($[-0.13,\, 0.13]$) $\quad$
  \\
  $\mbox{Im}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  \\[0.1cm]
  $\mbox{Re}(\wilson{S} + \wilson{S'})$
  & $[-0.36,\, 0.39]$ ($[-0.69,\, 0.68]$)
  & $-$
  & $[-0.32,\, 0.32]$ ($[-0.59,\, 0.62]$)
  \\
  $\mbox{Im}(\wilson{S} + \wilson{S'})$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  & $-$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} - \wilson{P'})$
  & $-$
  & $[ 0.05,\, 0.20]$ ($[ 0.01,\, 0.26]$)
  & $[ 0.00,\, 0.16]$ ($[-0.07,\, 0.22]$)
  \\
  $\mbox{Im}(\wilson{P} - \wilson{P'})$
  & $-$
  & \eos{$[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$)}
  & \eos{$[-0.10,\, 0.10]$ ($[-0.20,\, 0.20]$)}
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} + \wilson{P'})$
  & $[-0.24,\, 0.51]$ ($[-0.51,\, 0.82]$)
  & $-$
  & $[-0.12,\, 0.52]$ ($[-0.42,\, 0.78]$)
  \\
  $\mbox{Im}(\wilson{P} + \wilson{P'})$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  & $-$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cSP:1-dimCLs}
     The 1D-marginalized constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
     at 68\% (95\%) probability from measurements of $i)$ only $F_H^\mu$,
     $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$ all the data in
     \reftab{tab:observables} and additional new physics contributions to
     $\wilson{9,\, 9',\, 10,\,10'}$.
  }
\end{table*}

@@

Interference terms of $\wilson{P,\,P'}$ with vectorial couplings might weaken
these bounds. Most important for $\overline{\cal B}(B_s \to \bar\mu\mu)$ are
$(\wilson{10} - \wilson{10'})$ --- compare \refeq{eq:Br-Bsmumu:time0} --- and
for $F_H^\ell$ similarly $(\wilson{10} + \wilson{10'})$ \cite{Bobeth:2007dw},
which are suppressed by factors $m_\mu/M_{B_s}$ and $m_\mu/\sqrt{q^2}$,
respectively. However, due to the large SM contribution of $\wilson[SM]{10}
\simeq -4.2$, these terms are important for small pseudo-scalar couplings.
We compile constraints on complex-valued scalar couplings from $i)$ only
$F_H^\mu$, $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$
their combination with all the other observables in \reftab{tab:observables},
even allowing new physics in vectorial couplings
$\wilson{9,\ 9',\, 10,\, 10'}$ in \reftab{tab:cSP:1-dimCLs}, utilising
\todo{uniform priors for $\mbox{Re, Im}(\wilson{i}) \in[-7,\, 7]$}.
Neither $F_H^\ell$ nor $\overline{\cal B}(B_s \to \bar\mu\mu)$
alone can bound all four complex-valued scalar couplings, however their
combination is capable to do so and moreover, the bounds are stable against
destructive interference with vectorial couplings. In the general case
of complex-valued couplings, $\overline{\cal B}(B_s \to \bar\mu\mu)$ does
not provide anymore constraints on sub-intervals in contrast to the
case of real-valued couplings. In consequence, for example the ring-like
structure in the $(\wilson{S}-\wilson{S'}) - (\wilson{P}-\wilson{P'}) $-plane
of \reffig{fig:scalar} would turn into a filled circle.

@@

In the following we consider a model-independent scenario as predicted by the SM
augmented by dimension six operators that respect the SM gauge group and are
composed out of SM fields. After the discovery of a scalar resonance at the LHC
that complies currently with all requirements of the Higgs particle in the SM
and the steadily rising lower bounds on new particle masses towards higher energies
from ATLAS and CMS such a scenario becomes more and more viable.

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{cc|c|ccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $9,10,T,T5$
  & $10^{(')},S^{(')},P^{(')}$
  & $10^{(')},S^{(')},P^{(')},T,T5$
  \\
  \hline \hline
  \multirow{2}{*}{$J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & \eos{$(-1.27_{-0.64}^{+3.08}) \cdot 10^{-21}$}
  & \eos{$( 0.01_{-0.12}^{+0.06}) \cdot 10^{-21}$}
  & \eos{$( 0.71_{-1.98}^{+0.52}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & \eos{$(-0.43_{-0.25}^{+1.06}) \cdot 10^{-21}$}
  & \eos{$(-0.03_{-0.00}^{+0.02}) \cdot 10^{-21}$}
  & \eos{$(-0.25_{-0.23}^{+0.72}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$J_{1c} + J_{2c}$}
  & $[1.1,\, 6]$
  & \eos{$(1.80_{-0.26}^{+0.30}) \cdot 10^{-21}$}
  & \eos{$(3.05_{-0.96}^{+1.31}) \cdot 10^{-21}$}
  & \eos{$(1.22_{-0.17}^{+0.26}) \cdot 10^{-21}$}
  & \eos{$(3.23_{-1.31}^{+2.36}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & \eos{$(8.75_{-1.82}^{+2.05}) \cdot 10^{-23}$}
  & \eos{$(5.63_{-2.58}^{+3.29}) \cdot 10^{-21}$}
  & \eos{$(7.49_{-2.02}^{+1.01}) \cdot 10^{-23}$}
  & \eos{$(7.28_{-3.29}^{+5.17}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$J_{1s} - 3 J_{2s}$}
  & $[1.1,\, 6]$
  & \eos{$(2.04_{-0.50}^{+0.57}) \cdot 10^{-22}$}
  & \eos{$(1.46_{-0.60}^{+0.76}) \cdot 10^{-20}$}
  & \eos{SM}
  & \eos{$(2.00_{-0.97}^{+1.03}) \cdot 10^{-20}$}
  \\
  & $[15,\, 19]$
  & \eos{$(5.99_{-1.08}^{+1.19}) \cdot 10^{-23}$}
  & \eos{$(6.57_{-2.72}^{+3.40}) \cdot 10^{-21}$}
  & \eos{SM}
  & \eos{$(9.29_{-4.54}^{+3.86}) \cdot 10^{-21}$}
  \\
  \hline \hline
  \multicolumn{2}{c|}{$A_{\Delta \Gamma}$}
  & 1
  &
  & SM
  &
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The 68\% probability intervals of not yet measured angular observables in
     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$
     for several new physics scenarios respecting all the considered experimental
     constraints. The SM prior predictives are given too, where ``$\simeq 0$''
     indicates zero in the considered
     approximation, see text for more explanations.
  }
\end{table*}

@@

For comparison, the SM estimates are also given in \reftab{tab:postdictions}.
At low-$q^2$ they are of order ${\cal O}(10^{-21})$ for $(J_{1s} - 3\, J_{2s})$ and
$(J_{1c} + J_{2c})$, getting suppressed down to ${\cal O}(10^{-23})$ at high-$q^2$
due to the $m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical
magnitude of vectorial couplings, note that for example the decay width of
$B\to K^*\bar\ell\ell$
\begin{align}
  \frac{{\rm d}\Gamma}{{\rm d}q^2} & =
    \frac{2}{3} (3 J_{1s} - J_{2s}) + \frac{1}{3} (3 J_{1c} -  J_{2c})
\end{align}
is numerically of the order ${\cal O}(10^{-19})$ in the SM
\begin{equation}
\begin{aligned}
  \langle {\rm d}\Gamma/{\rm d}q^2 \rangle_{[1.1,\, 6]} & =
  \eos{\left(1.07_{-0.25}^{+0.28} \right) \cdot 10^{-19}} \,,
\\
  \langle {\rm d}\Gamma/{\rm d}q^2 \rangle_{[\eos{16},\, 19]} & =
  \eos{\left(0.63_{-0.17}^{+0.20} \right) \cdot 10^{-19}} \,,
\end{aligned}
\end{equation}
when integrated over low- and high-$q^2$ regions. On the other hand, $J_{6c}$
is strictly zero for the approximation adopted here. Non-zero contributions
can be generated by QED corrections or potentially from higher-dimensional
($d > 6$) $|\Delta B| = |\Delta S| = 1$ operators, leading to parametrical
suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$, respectively. Such a
suppression must be compared to potential suppression present for tensorial
and scalar contributions in particular NP models in order to decide their
relevance. Our model-independent fits are still in a realm where such
considerations are insignificant since current experimental measurements, in
combination with theory uncertainties, do not impose yet too stringent
constraints on tensorial and scalar couplings.

>>>>

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
  %\includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \caption{ The sensitivity to the tensorial coupling
      $\wilson{T}$ of $F_H$ [first row] and ${\cal B}$ [second row] in
      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ [fifth row] in $B^0 \to K^{*0}
      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
      last two rows, the observables are normalized by the lifetime of
      the $B$ meson for easier comparison with the branching
      ratios. The bands represent the theory uncertainties at 68\%
      and 95\% probability.  For comparison, two sets of bands are
      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
      latest 68\% uncertainty reported by LHCb (grey) if a measurement
      is available. 
      \todo{Perhaps restrict plots to range $C_T \in [-0.7, +0.7]$ 
            or even $\in [-0.5, +0.5]$?}}
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
%\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & only $\overline{\cal B}(B_s \to \bar\mu\mu)$
  & all
  \\
  set of couplings
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P',\,9,\,9',\,10,\,10'}$
  \\
  \hline \hline
  $\mbox{Re}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & $\quad$ $[-0.10,\, 0.08]$ ($[-0.14,\, 0.13]$) $\quad$
  & $\quad$ $[-0.08,\, 0.07]$ ($[-0.13,\, 0.13]$) $\quad$
  \\
  $\mbox{Im}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & $\quad$ $[-0.07,\, 0.07]$ ($[-0.11,\, 0.12]$) $\quad$
  & $\quad$ $[-0.07,\, 0.07]$ ($[-0.12,\, 0.11]$) $\quad$
  \\[0.1cm]
  $\mbox{Re}(\wilson{S} + \wilson{S'})$
  & $[-0.36,\, 0.39]$ ($[-0.69,\, 0.68]$)
  & $-$
  & $[-0.32,\, 0.32]$ ($[-0.59,\, 0.62]$)
  \\
  $\mbox{Im}(\wilson{S} + \wilson{S'})$
  & $[-0.37,\, 0.35]$ ($[-0.68,\, 0.66]$)
  & $-$
  & $[-0.25,\, 0.41]$ ($[-0.57,\, 0.64]$)
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} - \wilson{P'})$
  & $-$
  & $[ 0.05,\, 0.20]$ ($[ 0.01,\, 0.26]$)
  & $[ 0.00,\, 0.16]$ ($[-0.07,\, 0.22]$)
  \\
  $\mbox{Im}(\wilson{P} - \wilson{P'})$
  & $-$
  & $[-0.07,\, 0.08]$ ($[-0.12,\, 0.12]$)
  & $[-0.07,\, 0.09]$ ($[-0.14,\, 0.16]$)
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} + \wilson{P'})$
  & $[-0.24,\, 0.51]$ ($[-0.51,\, 0.82]$)
  & $-$
  & $[-0.12,\, 0.52]$ ($[-0.42,\, 0.78]$)
  \\
  $\mbox{Im}(\wilson{P} + \wilson{P'})$
  & $[-0.36,\, 0.37]$ ($[-0.67,\, 0.67]$)
  & $-$
  & $[-0.37,\, 0.29]$ ($[-0.68,\, 0.57]$)
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cSP:1-dimCLs}
     The 1D-marginalized constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
     at 68\% (95\%) probability from measurements of $i)$ only $F_H^\mu$,
     $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$ all the data in
     \reftab{tab:observables} and additional new physics contributions to
     $\wilson{9,\, 9',\, 10,\,10'}$.
  }
\end{table*}

@@

Interference terms of $\wilson{P,\,P'}$ with vectorial couplings might weaken
these bounds. Most important for $\overline{\cal B}(B_s \to \bar\mu\mu)$ are
$(\wilson{10} - \wilson{10'})$ --- compare \refeq{eq:Br-Bsmumu:time0} --- and
for $F_H^\ell$ similarly $(\wilson{10} + \wilson{10'})$ \cite{Bobeth:2007dw},
which are suppressed by factors $m_\mu/M_{B_s}$ and $m_\mu/\sqrt{q^2}$,
respectively. However, due to the large SM contribution of $\wilson[SM]{10}
\simeq -4.2$, these terms are important for small pseudo-scalar couplings.
We compile constraints on complex-valued scalar couplings from $i)$ only
$F_H^\mu$, $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$
their combination with all the other observables in \reftab{tab:observables},
even allowing new physics in vectorial couplings
$\wilson{9,\ 9',\, 10,\, 10'}$ in \reftab{tab:cSP:1-dimCLs}, utilising
uniform priors for $\mbox{Re, Im}(\wilson{i}) \in[-7,\, 7]$.
Neither $F_H^\ell$ nor $\overline{\cal B}(B_s \to \bar\mu\mu)$
alone can bound all four complex-valued scalar couplings, however their
combination is capable to do so and moreover, the bounds are stable against
destructive interference with vectorial couplings. In the general case
of complex-valued couplings, $\overline{\cal B}(B_s \to \bar\mu\mu)$ does
not provide anymore constraints on sub-intervals in contrast to the
case of real-valued couplings. In consequence, for example the ring-like
structure in the $(\wilson{S}-\wilson{S'}) - (\wilson{P}-\wilson{P'}) $-plane
of \reffig{fig:scalar} would turn into a filled circle.

@@

In the following we consider a model-independent scenario as predicted by the SM
augmented by dimension six operators that respect the SM gauge group and are
composed out of SM fields. After the discovery of a scalar resonance at the LHC
that complies currently with all requirements of the Higgs particle in the SM
and the steadily rising lower bounds on new particle masses towards higher energies
from ATLAS and CMS such a scenario becomes more and more viable\footnote{\todo{
comment on Cata/Jung \cite{Cata:2015ltad}.}}.

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{cc|c|ccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $T,\,T5,\,9,\,10,$
  & $S^{(')},\,P^{(')},\,9^{(')},\,10^{(')}$
  & $S^{(')},P^{(')},\,T,\,T5,\,9^{(')},10^{(')}$
  \\
  \hline \hline
  \multirow{2}{*}{$\tau_{B^0} \times J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & $(0.7_{-2.1}^{+1.7}) \cdot 10^{-9\;}$
  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-10}$
  & \eos{$( 0.71_{-1.98}^{+0.52}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & $(2.1_{-6.2}^{+5.1}) \cdot 10^{-10}$
  & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
  & \eos{$(-0.25_{-0.23}^{+0.72}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1c} + J_{2c})$}
  & $[1.1,\, 6]$
  & $(3.54_{-0.66}^{+0.65}) \cdot 10^{-9\;}$
  & $(5.0_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
  & $(2.9_{-0.5}^{+0.4}) \cdot 10^{-9\;}$
  & \eos{$(3.23_{-1.31}^{+2.36}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $(1.72_{-0.16}^{+0.16}) \cdot 10^{-10}$
  & $(4.7_{-2.6}^{+3.3}) \cdot 10^{-9\;}$
  & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
  & \eos{$(7.28_{-3.29}^{+5.17}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1s} - 3 J_{2s})$}
  & $[1.1,\, 6]$
  & $(2.98_{-0.54}^{+0.63}) \cdot 10^{-10}$
  & $(1.9_{-1.1}^{+1.4}) \cdot 10^{-8\;}$
  & $(4.9_{-1.4}^{+1.6}) \cdot 10^{-10}$
  & \eos{$(2.00_{-0.97}^{+1.03}) \cdot 10^{-20}$}
  \\
  & $[15,\, 19]$
  & $(1.12_{-0.10}^{+0.10}) \cdot 10^{-10}$
  & $(7.1_{-3.8}^{+5.6}) \cdot 10^{-9\;}$
  & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
  & \eos{$(9.29_{-4.54}^{+3.86}) \cdot 10^{-21}$}
  \\
  \hline \hline
  \multicolumn{2}{c|}{$A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$}
  & 1
  & SM
  & $[-1,\, 1]$
  & \eos{???}
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The 68\% probability intervals of not yet measured angular observables in
     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$
     for several new physics scenarios respecting all the considered experimental
     constraints. The SM prior predictives are given too, where ``$\simeq 0$''
     indicates zero in the considered
     approximation, see text for more explanations.
  }
\end{table*}

@@

For comparison, the SM estimates are also given in \reftab{tab:postdictions}
multiplied by the $B^0$-meson life time $\tau_{B^0} = 1.519$~ps.
At low-$q^2$ they are of order ${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and
$(J_{1c} + J_{2c})$, getting suppressed down to ${\cal O}(10^{-10})$ at high-$q^2$
due to the $m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical
magnitude of vectorial couplings, note that for example the branching ratio of
$B\to K^*\bar\ell\ell$ 
\begin{align}
  \frac{1}{\tau_{B^0}} \frac{{\rm d}\BR}{{\rm d}q^2} & =
    \frac{2}{3} (3 J_{1s} - J_{2s}) + \frac{1}{3} (3 J_{1c} -  J_{2c})
\end{align}
is numerically of the order ${\cal O}(10^{-19})$ in the SM 
\todo{check large SM uncertainty of 30\% at low-$q^2$}
\begin{equation}
\begin{aligned}
  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[1.1,\, 6]} & =
  \left(1.86_{-0.44}^{+0.53} \right) \cdot 10^{-7} \,,
\\
  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[15,\, 19]} & =
  \left(1.91_{-0.16}^{+0.16} \right) \cdot 10^{-7} \,,
\end{aligned}
\end{equation}
when integrated over low- and high-$q^2$ regions. On the other hand, $J_{6c}$
is strictly zero for the approximation adopted here. Non-zero contributions
can be generated by QED corrections or potentially from higher-dimensional
($d > 6$) $|\Delta B| = |\Delta S| = 1$ operators, leading to parametrical
suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$, respectively. Such a
suppression must be compared to potential suppression present for tensorial
and scalar contributions in particular NP models in order to decide their
relevance. Our model-independent fits are still in a realm where such
considerations are insignificant since current experimental measurements, in
combination with theory uncertainties, do not impose yet too stringent
constraints on tensorial and scalar couplings.
